Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
pagestyle plain
Sec. IV edited

\renewcommand{\iec}{i.e., }
\begin{document}

@@

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$.
Its starting time $st_v$ is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$.
The starting time is therefore:\\[-.7cm]

@@

    \medskip
    \noindent{\em Assignment of task~$v$.}\\
    Once we have computed all finish times for task~$v$,
    we keep the minimum $FT(v,p_j)$ and assign task~$v$
    to processor~$p_j$.
    In detail, we:
    \begin{itemize}
        \item  Evict the file memories that correspond to edge weights that need to be evicted to free the memory.
        We remove these files from pending memories
        $PD_j$, add them to pending data in the communication buffer, and reduce the available buffer size accordingly.
        \item    Calculate the new $availM_j$ on the processor.
        We subtract the weights of all incoming files from predecessors assigned to the same processor,
        and add the weights of outgoing files generated by the currently assigned task.
        \item  For every predecessor of~$v$ that has been assigned to another processor, we adjust ready times on
        communication buffers $rt_{j', j}$ for the processor~$j'$that the predecessor $u$ has been assigned to: we increase them by the
        communication time $c( u,v) / \beta$.
        We also remove the incoming files from either the pending memories or pending data in buffers of these other
        processors, and increase the available memories or available buffer sizes on these processors.
        \item We compute the correct amount of available memory for~$p_j$ (for when the task is done).
        Then, for each predecessor that is mapped to the same processor, 
        we remove the pending memory corresponding to the weight of
        the incoming edge, also freeing the same amount of available memory (increasing $availM_j$).
        For each successor, we rather add the edge weights to pending memories and reduce $availM_j$ 
        by the corresponding amount.
    \end{itemize}

>>>>

\renewcommand{\iec}{i.e., }

\pagestyle{plain}

\begin{document}

@@

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$.
Its starting time $st_v$ is dictated by the maximum between $rt_j$ and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$.
The starting time is therefore:\\[-.7cm]

@@

\medskip
\noindent{\em Assignment of task~$v$.}\\
Once we have computed all finish times for task~$v$,
we keep the minimum $FT(v,p_j)$ and assign~$v$
to processor~$p_j$. 
In detail:
\begin{itemize}
\item 
  We evict the files corresponding to edge weights that need to be evicted to free the memory.
  We remove these files from pending memories
  $PD_j$, add them to pending data in the communication buffer, and reduce the available buffer size accordingly.
\item 
  We calculate the new $availM_j$ on the processor.
  Next, we subtract the weights of all incoming files from predecessors assigned to the same processor
  and add the weights of outgoing files generated by the currently assigned task.

\item  
  For every predecessor of~$v$ that has been assigned to another processor, we adjust ready times on
  communication buffers $rt_{j', j}$ for the processor~$j'$ that the predecessor $u$ has been assigned to: we increase them by the
  communication time $c( u,v) / \beta$.
  We also remove the incoming files from either the pending memories or pending data in buffers of these other
  processors, and increase the available memory or buffer sizes on these processors.

\item 
  We compute the correct amount of available memory for~$p_j$ (for when the task is done).
  Then, for each predecessor that is mapped to the same processor, 
  we remove the pending memory corresponding to the weight of
  the incoming edge, also freeing the same amount of available memory (increasing $availM_j$).
  For each successor, we rather add the edge weights to pending memories and reduce $availM_j$ 
  by the corresponding amount.
\end{itemize}
